---
title: "Plotly"
author: "Sunil"
date: "October 2, 2019"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Simple plotly example - Student's Sleep  dataset

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Introduction

- This is as part of Week 3 of Coure 9 under Data science Specialisation
- Goal is to create a web page  presentation and feature an interactive plot that appears to have been created with Plotly
- Chosen the Student's Sleep dataset for this presentation.

## Slide with R Output

```{r sleep, echo = TRUE}
summary(sleep)
```

## Slide with Plot

```{r plot ,include=FALSE}
library(plotly)

f <- list(
  family = "Arial",
  size = 20,   color = "Blue" )
x <- list(
  title = "Group - Drug given ",   titlefont = f )
y <- list(
  title = "Increase in hours of sleep",   titlefont = f )
```

```{r plotly,warning=FALSE}
plot_ly(sleep, x = sleep$group, y=sleep$extra, type="box", showlegend=TRUE, 
     color=as.factor(sleep$group))%>%   
        layout(xaxis=x, yaxis=y)


```

## Interpretation
 - At a glance , we can see that the commercial airlines took off post worldwar.
 
 